### 2019-08-17 README.Rmd
remove second install method (master is kept synced with CRAN).

To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this developmental version is at <https://infer.netlify.com>.

```{r}
install.packages("remotes")
remotes::install_github("tidymodels/infer")
```

To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first. This version was last updated on `r Sys.time()`.

>>>>

To install the developmental version of `infer` (do so at your own risk), make sure to install `remotes` first.
